The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-27 paper/ms.tex
phrasing

Individual elemental abundances are derived by first fixing the stellar atmospheric parameters to those determined above. Spectra are then synthesized  in regions centered around an absorption  feature of the element we want to derive. The spectra generated will have different [X/Fe] values. A $\chi^2$ minimization procedure is then done to derive the best fitting abundance for each line. The reported abundances are the median [X/Fe] value of the various line regions for a given element. { \bf Ben: Maybe remove this if we do not actually implement line-by-line differential; Do we have a TRES Arcturus spectrum.} Abundance uncertainties reported are the standard error in the line-by-line abundance ratios. Where only one line exists for a given element, we conservatively assume the standard error is 0.10~dex. In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameter values and other systematic errors arising from incorrect line list data upon other things. We do note, however, thus use of asteroseismology really reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}. To achieve the most precise abundances we have derived them using  both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}. The results of these absolute abundance calculations {\bf without the line-by-line differential analysis implemented?}, are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}. Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material. No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.

>>>>

Individual elemental abundances are derived by first fixing the stellar atmospheric parameters to those determined above. Spectra are then synthesized  in regions centered around an absorption  feature of the element we want to derive. The spectra generated will have different [X/Fe] values. A $\chi^2$ minimization procedure is then done to derive the best fitting abundance for each line. The reported abundances are the median [X/Fe] value of the various line regions for a given element. { \bf Ben: Maybe remove this if we do not actually implement line-by-line differential; Do we have a TRES Arcturus spectrum.} Abundance uncertainties reported are the standard error in the line-by-line abundance ratios. Where only one line exists for a given element, we conservatively assume the standard error is 0.10~dex. In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameter values and other systematic errors arising, for instance, from incorrect line list data. We do note, however, thus use of asteroseismology really reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}. To achieve the most precise abundances we have derived them using  both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}. The results of these absolute abundance calculations {\bf without the line-by-line differential analysis implemented?}, are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}. Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material. No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.
